The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-09-26 manuscript/manuscript.qmd
Better fig-issue-preds

```{r fig-issue-preds, fig.width=6, fig.height=4.5}
#| include: true
#| echo: false
#| layout-ncol: 1
#| fig-cap: "Posterior predictions from ordered Beta regression model, conditional on organization issue area."
#| fig-subcap: 
#|   - "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis categories sum to 100% across the panels."
#|   - "Distribution of the expectation of posterior predictions. These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
preds_issue_plot <- preds_issue |> 
  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) |> 
  group_by(outcome, issue_area_nice, draw) |> 
  summarize(count = n()) |> 
  group_by(issue_area_nice, draw) |> 
  mutate(prop = count / sum(count)) |> 
  ungroup() |> 
  mutate(issue_area_nice = fct_reorder(issue_area_nice, prop))

# preds_issue_plot |>
#   group_by(outcome, issue_area_nice) |>
#   median_qi(prop)

ggplot(preds_issue_plot, aes(x = issue_area_nice, y = prop)) +
  stat_pointinterval(color = clrs[5], .width = 0.95, fatten_point = 1) +
  facet_wrap(vars(outcome), ncol = 1, scales = "free_y") +
  scale_x_discrete(labels = label_wrap(10)) +
  scale_y_continuous(labels = label_percent()) +
  labs(x = NULL, y = "Proportion of predictions",
       caption = "Point shows posterior median; lines show 95% credible interval") +
  theme_ongo()

epreds_issue |> 
  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
  mutate(issue_area_nice = fct_reorder(issue_area_nice, .epred)) |> 
  ggplot(aes(x = .epred, y = issue_area_nice)) +
  stat_halfeye(fill = clrs[5], .width = c(0.8, 0.95)) +
  scale_x_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(8, 32, 4))) +
  guides(fill = "none") +
  labs(x = "Expected proportion of provinces", y = NULL,
       caption = "Point shows posterior median; lines show 80% and 95% credible intervals") +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

>>>>

```{r fig-issue-preds, fig.width=8, fig.height=6}
#| include: true
#| echo: false
#| column: body-outset
#| fig-cap: "**Top**: Posterior predictions from ordered Beta regression model,
#|   conditional on organization issue area, showing the predicted proportion of
#|   INGOs working in 1 province, all 32 provinces, or somewhere in between. The
#|   vertical slices of the bars depict 500 posterior samples; the fuzziness
#|   represents the uncertainty in category boundaries. 95% credible intervals 
#|   are shown as ranges in each category **Bottom**: Expectation (or average) of
#|   posterior predictive distributions. These distributions take into account 
#|   single-province and nationwide predictions and represent the *overall*
#|   conditional average geographic range for INGOs."
preds_issue_plot <- preds_issue |> 
  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "Only 1 province",
    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
    .prediction == 1 ~ "All 32 provinces",
    .ptype = factor(
      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
      ordered = TRUE)
  )) |> 
  group_by(outcome, issue_area_nice, draw) |> 
  summarize(count = n()) |> 
  group_by(issue_area_nice, draw) |> 
  mutate(prop = count / sum(count))

preds_issue_plot_order <- preds_issue_plot |> 
  filter(outcome == "All 32 provinces") |>
  group_by(issue_area_nice) |> 
  summarize(median_prop = median(prop)) |> 
  arrange(median_prop) |> 
  mutate(issue_area_nice_labels = str_wrap(issue_area_nice, 15)) |> 
  mutate(issue_area_nice = fct_inorder(issue_area_nice))

preds_issue_text <- preds_issue_plot |> 
  group_by(outcome, issue_area_nice) |> 
  summarize(median_prop = median_qi(prop)) |> 
  unnest(median_prop) |> 
  group_by(issue_area_nice) |> 
  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
  mutate(y_plot = 1 - y_plot) |> 
  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
  mutate(prop_ci_nice = glue::glue(
    "{ymin}–{ymax}",
    ymin = label_number(accuracy = 1, scale = 100)(ymin),
    ymax = label_percent(accuracy = 1)(ymax)
  )) |> 
  mutate(issue_area_nice = factor(
    issue_area_nice, 
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  ))

p1 <- preds_issue_plot |> 
  mutate(issue_area_nice = factor(
    issue_area_nice, 
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  )) |> 
  ggplot(aes(x = draw, y = prop)) +
  geom_col(aes(fill = outcome), position = "stack", linewidth = 0, width = 1) +
  geom_text(
    data = preds_issue_text,
    aes(x = 250, y = y_plot, label = prop_ci_nice),
    size = 3, fontface = "bold", color = "white"
  ) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1) +
  labs(
    x = NULL, y = "Proportion of predictions", fill = NULL,
    title = "Overall expected proportion of type of geographic reach across issue area",
    subtitle = "Posterior predictions of outcome categories"
  ) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

p2 <- epreds_issue |>
  left_join(issue_indicator_lookup, by = join_by(issue_area)) |>
  mutate(issue_area_nice = factor(
    issue_area_nice,
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  )) |>
  ggplot(aes(x = issue_area_nice, y = .epred)) +
  stat_halfeye(fill = clrs[6], color = clrs[8]) +
  scale_x_discrete(labels = NULL) +
  scale_y_continuous(
    labels = label_percent(),
    sec.axis = sec_axis(
      trans = ~ prop_to_provinces(.),
      name = "Expected provinces",
      breaks = seq(2, 32, 6)
    )
  ) +
  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1, scales = "free_x") +
  guides(fill = "none") +
  labs(
    x = NULL, y = "Proportion of provinces",
    title = "Overall expected proportion of provinces",
    subtitle = "Expectation of posterior predictions"
  ) +
  theme_ongo() +
  theme(
    panel.grid.major.x = element_blank(),
    axis.ticks.y.right = element_line(linewidth = 0.25, color = "grey50"),
    axis.title.y.right = element_text(hjust = 0),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

(p1 / plot_spacer() / p2) +
  plot_layout(heights = c(0.65, 0.02, 0.33))
```
